The complex network of trophic interactions in a subAntarctic Marine Protected Area

### 2023-01-23 1st_Manuscript/ManuscriptDraft.Rmd
Page breaks

@@

```{r figure2, echo=FALSE, fig.align='center', fig.cap="Graph of the food web of MPA Namuncurá-Banco Burdwood. Circles represent the species and arrows the trophic interactions. Colour gradient indicate the trophic level. Circle diameter is relative to the number of interactions."}
# Food web graph

@@

plot <- plot_troph_level(g, vertexLabel = F, modules = F, ylab = "Trophic level")

@@

```{r figure3, echo=FALSE, fig.height = 28, fig.width = 20, fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group."}
# Degree distributions: network, predator, prey & group
# above row (network, prey, predator), below row (group)

@@

```{r figure5, echo=FALSE}
# Topological roles

top.role.col <- hcl.colors(4, palette = "Purple-Green")
TRColor <- setNames(top.role.col, levels(as.factor(V(g_up)$TopRole)))
TRColor <- as.data.frame(TRColor) %>% 
  mutate(TopRole = c("hubcon", "modcon", "modhub", "modspe"))
#show_col(top.role.col)  # shows color & code
data_TRColor <- spp_total %>% 
  dplyr::select(TopRole, everything()) %>% 
  left_join(TRColor)
g_up_c <- g_up %>% 
  set_vertex_attr("TRColor", value = data_TRColor$TRColor)

# Filter network connectors ('hubcon') & module connectors ('modcon'). Violet & pink respectively
sp_con <- spp_total %>% 
  filter(TopRole == "hubcon" | TopRole == "modcon")

# Move to a new page
grid.newpage()
# Arrange figure
figure_5 <- plot_troph_level(g_up_c, vertexLabel = F, modules = F, ylab = "Trophic level", vertex.color = V(g_up_c)$TRColor)

>>>>

\newpage

@@

```{r figure2, echo=FALSE, fig.align='center', fig.width = 20, fig.height=20, fig.cap="Graph of the food web of MPA Namuncurá-Banco Burdwood. Circles represent the species and arrows the trophic interactions. Colour gradient indicate the trophic level. Circle diameter is relative to the number of interactions."}
# Food web graph

@@

par(cex.axis=1.5, cex.lab=1.5)
plot <- plot_troph_level(g, vertexLabel = F, modules = F, ylab = "Trophic level")

@@

\newpage

```{r figure3, echo=FALSE, fig.height = 28, fig.width = 20, fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group. Groups are vertically ordered by trophic level."}
# Degree distributions: network, predator, prey & group
# above row (network, prey, predator), below row (group)

@@
